Transit time distributions.

### 2014-12-18 prep_figures/commute/commute-detail.Rmd
commute time plots

---
title: "Ricci and transit times"
runtime: shiny
output: html_document
---

@@

library(ggvis)
library(ape)
library(apTreeshape)

source("process.R")

# d <- get_results("../../results-rspr/commute-nodata/commute6.mat")
# d$dist <- as.factor(d$dist)

d5 <- get_results("../../results-rspr/commute-onesplit/123_45-1v5c.tsv")
d6 <- get_results("../../results-rspr/commute-onesplit/123_456-1v5c.tsv")
d <- d5

d %>%
  ggvis(x = ~kappa, y = ~MAT) %>%
  #ggvis(x = ~kappa, y = ~MCT) %>%
  layer_points() %>%
  # A dummy layer so that we can use text in the tooltip.
  layer_text(text := ~info, fontSize := 0) %>%
  add_axis("x", grid = FALSE) %>%
  add_axis("y", grid = FALSE) %>%
  add_tooltip(function(df) df$info)
```

>>>>

---
title: "Transit time distributions."
runtime: knitr
output: html_document
---

@@

library(ggplot2)

grab_data <- function(fname) {
  df <- read.table(fname, stringsAsFactors = FALSE)
  colnames(df) <- c("t1", "t2", "time", "count")
  df$cmp <- paste(df$t1, df$t2)
  df$dens <- df$count / sum(df$count)
  df
}

d <- rbind(
  grab_data("runs/run1-uniq_trees_T-col-CCC1_2D_3D_C4_5DD-CC1_C2_3DD_C4_5DD.tab"),
  grab_data("runs/run1-uniq_trees_T-col-CCCC1_2D_3D_4D_5D-CCCC1_2D_3D_5D_4D.tab"),
  grab_data("runs/run1-uniq_trees_T-col-CCCC1_2D_3D_4D_5D-CCC1_2D_3D_C4_5DD.tab"))

sub_d <- subset(d, t1 != t2)

ggplot(sub_d, aes(x=time, y=dens, color=cmp)) + geom_line() + scale_x_continuous(limits=c(0,100))
```
